Towards the construction of a causal map of the human phenome

### 2017-06-27 docs/manuscript.tex
updated

\setlength{\droptitle}{-2em}
  \title{Towards the construction of a causal map of the human phenome}
  \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
  \author{}
  \preauthor{}\postauthor{}
  \predate{\centering\large\emph}
  \postdate{\par}
  \date{26 June 2017}

@@

\subsubsection{Graph database}\label{graph-database}

@@

@@

Number of associations using different approaches Which methods were
preferentially chosen

@@

@@

  \begin{itemize}
  \tightlist
  \item
    Impossible causal associations
  \item
    Temporal effects
  \item
    Risk liability etc
  \item
    Single variants
  \end{itemize}
\item
  Further developments required to improve causal estimates
\item
  The use of causal chains to improve power
\end{itemize}

>>>>

\setlength{\droptitle}{-2em}
  \title{Towards the construction of a causal map of the human phenome}
  \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
  \author{}
  \preauthor{}\postauthor{}
  \predate{\centering\large\emph}
  \postdate{\par}
  \date{27 June 2017}

@@

\subsubsection{Graph database of MR
estimates}\label{graph-database-of-mr-estimates}

@@

We evaluated the efficacy of the Steiger filtering approach for
improving MR reliability using 200,000 simulated datasets for in which
there were varying null and non-null causal relationships, as well as
varying degrees of instrument strength, sample size and forms of
horizontal pleiotropy. Compared to

@@

The gating function for the mixture of experts model was trained by
generating a different random forest independently for each of the 28 MR
approaches, using a random two-thirds of the simulated datasets. The
prediction accuracy of the performance for each of these methods is
shown in table X, estimated using the remaining third of datasets. The
dataset characteristics with the most importance for each of the
predictors is also shown, as well as the frequency for which each of the
methods was selected in the testing datasets.

@@

It is important to note that though the gating function should be
applicable to datasets of any distribution of characteristics, the
frequencies of chosen methods are relative to the characteristics of the
simulated datasets, and would not necessarily be the same frequencies
observed empirically. Applying the MoE model to the X number of MR
associations for which there was sufficient data, we found that

@@

  \begin{itemize}
  \tightlist
  \item
    Impossible causal associations
  \item
    Temporal effects
  \item
    Risk liability etc
  \item
    Single variants
  \end{itemize}
\item
  Further developments required to improve causal estimates
\item
  The use of causal chains to improve power
\item
  Repository will continually update - need to time stamp and provide
  access to older associations
\end{itemize}

\subsection{Figures}\label{figures}

\newpage

\includegraphics{images/fig1.pdf}

\newpage

\includegraphics{images/fig2.pdf}
